Why does preregistration increase the persuasiveness of evidence? A Bayesian rationalization.

### 2022-08-19 manuscript.Rmd
Update manuscript.Rmd

We argue that experiment 1 has high theoretical risk ($P(¬E_1|¬H)$) and high detectability ($P(E_1|H)$).
If "insight" has nothing to do with solving the problem ($¬H$), then presenting the insight that Roman numerals could be used, should not lead to all students solving the problem ($¬E_1$); the experiment therefore has high theoretical risk ($P(¬E_1|¬H)$)
Conversely, if insight is required to solve the problem ($H$), then it is likely to help all students to solve the problem ($E_1$), the experiment therefore has high detectability ($P(E_1|H)$).
The second experiment, on the other hand, has low theoretical risk ($P(¬E_2|¬H)$).
Even if "insight" has nothing to do with solving the problem ($¬H$), there are other plausible reasons for observing the evidence ($E_2$), because the students could simply copy the solution, without having any insight.
With regard to detectability, experiments 1 and 2 differ in no obvious way.
Experiment 3, however, also has low detectability.
It is unlikely that all students come up with the correct solution in a short time ($E_3$), even if insight is required ($H$) experiment 3 therefore has low detectability ($P(E_3|H)$).
The theoretical risk, however, is also low in absolute terms, but high compared to the detectability.
In the unlikely event that all 10 students place their matches to form the Roman numeral Ⅷ ($E_3$), it is probably due to insight ($H$) and not by chance $P(¬E_2|¬H)$).
Of course, in practice, we would allow the evidence to be probabilistic, e.g., relax the requirement of "all students" to nine out of ten students, more than eight, and so forth.
<!-- I think this example needs to be swapped for a better one. For example: H: A coin is fair. E1: Observe if the person throwing the coin is betwenn 0 and 10 meters in height (high detectability, no theoretical risk). E2: Throw the coin 2 times and observe if it lands one time on heads and one time on
As argued earlier, the remainder of the paper will focus on binary, non-probabilisitic evidence to keep the mathematical notation as simple as possible.
We discuss the relation between statistical methods and theoretical risk in the [Statistical Methods] section.

>>>>

We argue that experiment 1 has high theoretical risk ($P(¬E_1|¬H)$) and high detectability ($P(E_1|H)$).
If "insight" has nothing to do with solving the problem ($¬H$), then presenting the insight that Roman numerals could be used, should not lead to all students solving the problem ($¬E_1$); the experiment therefore has high theoretical risk ($P(¬E_1|¬H)$)
Conversely, if insight is required to solve the problem ($H$), then it is likely to help all students to solve the problem ($E_1$), the experiment therefore has high detectability ($P(E_1|H)$).
The second experiment, on the other hand, has low theoretical risk ($P(¬E_2|¬H)$).
Even if "insight" has nothing to do with solving the problem ($¬H$), there are other plausible reasons for observing the evidence ($E_2$), because the students could simply copy the solution, without having any insight.
With regard to detectability, experiments 1 and 2 differ in no obvious way.
Experiment 3, however, also has low detectability.
It is unlikely that all students come up with the correct solution in a short time ($E_3$), even if insight is required ($H$) experiment 3 therefore has low detectability ($P(E_3|H)$).
The theoretical risk, however, is also low in absolute terms, but high compared to the detectability.
In the unlikely event that all 10 students place their matches to form the Roman numeral Ⅷ ($E_3$), it is probably due to insight ($H$) and not by chance $P(¬E_2|¬H)$).
Of course, in practice, we would allow the evidence to be probabilistic, e.g., relax the requirement of "all students" to nine out of ten students, more than eight, and so forth.
<!-- I think this example needs to be swapped for a simpler one. For example: H: A coin is fair. E1: Observe if the person throwing the coin is betwenn 0 and 10 meters in height (high detectability, no theoretical risk). E2: Throw the coin 2 times and observe if it lands one time on heads and one time on tails (detectability: P(E|H) = 0.5, theoretical risk: P(E|p != 0.5) = 1/3) E3: throw the coin 200 times, compute #heads/#200, construct a test (high power -> high detectability, high theoretical risk). -->
As argued earlier, the remainder of the paper will focus on binary, non-probabilisitic evidence to keep the mathematical notation as simple as possible. <!-- what is non-probabilistic evidence supposed to be? Evidence is always a random variable -->
We discuss the relation between statistical methods and theoretical risk in the [Statistical Methods] section.
